Blas\'e3D

### 2023-11-05 paper/paper2/ms.tex
Comment out deluxetable for now
Add back in the resample operator as a command
Add interpolated grid

\usepackage{amsmath}
\usepackage{blindtext}
% Temporary packages
\usepackage{mdframed}

@@

\appendix
\section{Linear Regression}
\blindtext

>>>>

\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{bm}
% Temporary packages
\usepackage{mdframed}
\usepackage{verbatim}

\DeclareMathOperator{\resample}{resample}

\def\Teff{T_{\rm eff}}
\def\vsini{v\sin{i}}
\def\kmps{\mathrm{km}\;\mathrm{s}^{-1}}

@@

\appendix
\section{Notation}
We adopt a mostly similar notation to the blas\'e paper, with some modifications.

\begin{deluxetable}{cp{10cm}}[h]
    \tabletypesize{\small}
    \tablecaption{Notation used in this paper\label{table2}}
    \tablehead{
        \colhead{Symbol} & \colhead{Meaning}
    }
    \startdata
    \hline
    \multicolumn{2}{c}{Indexes}\\
    \hline
    $i$ & Pixel index of the precomputed spectrum\\
    $j$ & Spectral line index\\
    $k$ & Grid point index\\
    \hline
    \multicolumn{2}{c}{Spectra}\\
    \hline
    $\bm{\lambda}$ & Native wavelength coordinate axis of the PHOENIX model grid\\
    $\mathsf{S}_k$ & Flux values of the $k^{th}$ precomputed spectrum\\
    $\mathsf{P}_k$ & Smooth polynomial to refine continuum-normalization\\
    $\mathsf{S}$ & Continuum normalized augmentation of $\mathsf{S}_{\rm abs}$\\
    $\mathsf{T}$ & Transmission values of the precomputed synthetic telluric model \\
    $\mathsf{D}$ & The observed data spectrum flux values\\
    $\bm{\epsilon}$ & The estimated uncertainties in the data spectrum\\
    $\mathsf{S}_{\rm clone}$ & Evaluable and tunable cloned flux model of $\mathsf{S}$\\
    $\mathsf{T}_{\rm clone}$ & Evaluable and tunable cloned transmission model of $\mathsf{T}$\\
    $\mathsf{S}_{\rm ext}$ & An augmentation of $\mathsf{S}_{\rm clone}$ with $v\sin{i}$ convolution and $RV$ translation\\
    $\mathsf{M}_{\rm joint}$ & The joint stellar and telluric model: $\mathsf{S}_{\rm ext} \odot \mathsf{T}_{\rm clone}(\bm{\lambda}_S)$ \\
    $\mathsf{M}$ & Joint model convolved
    with instrumental kernel and resampled to $\bm{\lambda}_D$\\
    $\mathsf{R}$ & The residual spectrum between a pair of inputs, \emph{e.g.} $\mathsf{D} - \mathsf{M}$\\
    $\bm{v}$ & The spectral coordinate axis $\bm{\lambda}$ expressed as a velocity difference\\
    \hline
    \multicolumn{2}{c}{Line properties}\\
    \hline
    $\lambda_{\mathrm{c},j}$ & Line center position of the $j^{th}$ spectral line\\
    $a_j$ & Gaussian line profile amplitude of the $j^{th}$ spectral line \\
    $\sigma_j$ & Gaussian line profile scale of the $j^{th}$ spectral line\\
    $\gamma_j$ & Lorentzian line profile half width of the $j^{th}$ spectral line\\
    $\mathsf{V}_j$ & The Voigt profile of the $j^{th}$ spectral line \\
    $\bar{\bm{F}}\bar{F}$ & The dense $(N_{\rm lines} \times N_{x})$ matrix of all line fluxes stacked vertically \\
    $\hat{\bm{F}}$ & The sparse $(N_{\rm lines} \times N_{\rm sparse})$ matrix of all line fluxes stacked vertically \\
    $\zeta$ & The rotational broadening convolution kernel\\
    $g$ & The instrumental broadening convolution kernel, typically a Gaussian\\
    \hline
    \multicolumn{2}{c}{Scalars}\\
    \hline
    $N_{\rm lines}$ & Number of spectral lines \\
    $N_{x}$ & Number of pixel coordinates in the precomputed spectrum $\bm{\lambda}_x$\\
    $N_{\rm sparse}$ & Number of non-zero pixels computed in the sparse implementation\\
    $\pm \Delta \lambda_{\mathrm{buffer}}$ & Buffer exceeding the red and blue limits of the data spectrum\\
    $P_{\rm rom}$ & The prominence threshold of spectral lines to include in cloning \\
    $v\sin{i}$ & Rotational broadening for stellar inclination $i$ and equatorial velocity $v$\\
    $RV$ & Radial velocity of the star\\
    $R$ & Spectrograph resolving power $\lambda/\delta\lambda$\\
    $\mathcal{L}$ & The loss scalar, usually the sum of the squares of the residuals\\
    \hline
    \multicolumn{2}{c}{Operators}\\
    \hline
    $\resample \big[ \mathsf{F(\bm{\lambda}_x)} \big]$ & The resample operator, takes in a flux spectrum $\mathsf{F}$ evaluated at $\bm{\lambda}_x$ coordinates and returns the mean flux within the pixel boundaries of coordinate $\bm{\lambda}_z$\\
    $*$& The convolution operator\\
    $\odot$& \emph{Hadamard product}, an elementwise product of two same-length vectors\\
    \enddata
\end{deluxetable}
